\chapter*{Abstract}

\vspace{2cm}

\noindent The application development for smartphone is currently increasing due to the amount of new smartphone coming to the market. A lot of these smartphones uses the new Google operating system : Android, launched just 2 years ago. It is promised to a huge future. Therefore, it is very interesting for students to learn about these new technologies.

\noindent The purpose of this project is to see what are the possibilities and the future of the smartphone Operating System Andoid. For that, it was necessary to install the tools needed to develop an Android application, learn how to use them and then test some simple examples of applications. Another goal is to compare the differences between an application developed for PCs and one developed for smartphone, and then learn about it in order to develop an application.

\noindent A real application, then, was developed during the project, it is a classic task manager that allows a user to better organize. This application has the main advantage, compared to other applications, the possibility of synchronize tasks with a remote server. The achievement of this project is divided in two parts : the development of the Android application and the development of the remote server to synchronize tasks with the smartphone. The application was developed using the \textit{eclipse} software and using the \textit{Java} language. The remote server uses a \textit{PHP/MySQL} server and converts the data transferred in \textit{JSON} format.

\noindent This project was very beneficial because it acquired new knowledges about the Android platform and point of view of the programming the Limitations and the possibilities it offers. This application may be published on the android market so that all users in the world can install and use.

\clearpage
\newpage