\chapter*{Glossary}
\addcontentsline{toc}{chapter}{Glossary}

\vspace{2cm}

\noindent \textbf{IDE} : (Integrated Development Environment) this is a software application that provides comprehensive facilities to computer programmers for software development. An IDE normally consists of a source code editor, a compiler and/or an interpreter, build automation tools and a debugger.

\vspace{3mm}

\noindent \textbf{JSON} : (JavaScript Object Notation) this is a lightweight text-based open standard designed for human-readable data interchange.

\vspace{3mm}

\noindent \textbf{MySQL} : this is a relational database management system that runs as a server providing multi-user access to a number of databases.

\vspace{3mm}

\noindent \textbf{PHP} : (Hypertext Preprocessor) this is a general-purpose scripting language originally designed for web development to produce dynamic web pages.

\vspace{3mm}

\noindent \textbf{Proxy server} : this is a server (a computer system or an application) that acts as an intermediary for requests from clients seeking resources from other servers.

\vspace{3mm}

\noindent \textbf{SDK} : (Software Development Kit) this is typically a set of development tools that allows for the creation of applications for a certain software package, software framework, hardware platform, computer system, video game console, operating system, or similar platform.

\vspace{3mm}

\noindent \textbf{Smartphone} : this is a mobile phone that offers more advanced computing ability and connectivity than a contemporary feature phone.

\vspace{3mm}

\noindent \textbf{SQLite} : this is an embedded relational database management system contained in a relatively small programming library.


\clearpage
